%-------------------------
% Resume in Latex
% Author : Xing Liu
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{
    {\normalsize #1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large #1} & {\large #2} \\
      \textit{\large #3} & \textit{\large #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\large #1} & {\large #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{
  \item{
    \textbf{\normalsize #1}{\normalsize : #2 \vspace{-4pt}}
  }
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  Resume STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/xingliu14/}{\huge Xing Liu}} & {\large Website:} \href{https://xingliu14.github.io/}{\large https://xingliu14.github.io/} \\
  {\large Email:} \href{mailto:xingliu14@gmail.com}{\large xingliu14@gmail.com} & {\large Mobile: +1-346-221-9933} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{\Large Professional Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Google}{Mountain View, CA}
      {Software Engineer}{Sept. 2021 - present}
      \resumeItemListStart
        \resumeItem{Led large-scale LLM optimization projects for Google Shopping, a role that involved creating and managing Gemini serving configurations for a portfolio of over 20 clients. Delivered a 2,000+ TPU reduction in resource consumption by applying sophisticated techniques like EEVEE MTP and KV Cache quantization, directly contributing to faster online inference and higher offline processing throughput}
        \resumeItem{Gemini 2.0 Flash Quantization: implemented and applied int4 weight quantization to FFW layers and int8 weight quantization to ATTN layers to Gemini 2.0 Flash decode serving workload at the TPU HLO layer, with sub-channel config, achieved neutral quality and 1.1x speedup}
        \resumeItem{StableHLO Quantizer: Lead the design and implementation of a neural network \href{https://github.com/tensorflow/tensorflow/tree/master/tensorflow/compiler/mlir/quantization}{Quantizer (open-sourced)} at StableHLO level. This is a compiler-level quantizer that provides robust cross-framework quantization capabilities with hardware optionality}
        \resumeItem{Developed and optimized a core server infrastructure for Google Shopping LLM services, enabling advanced features like real-time streaming and a sophisticated caching mechanism. Engineered the system to perform configurable TnS checks, ensuring secure and compliant service delivery}
      \resumeItemListEnd

    \resumeSubheading
      {Yahoo}{Sunnyvale, CA}
      {Software Engineer}{Mar. 2019 - Sept. 2021}
      \resumeItemListStart
        \resumeItem{Comm Channel Reputation Datasets: Implemented a data mining pipeline to generate reputation scores for 1.8B comm channels (email addresses/phone numbers), aggregated comm channel reputation data to produce comm channel groups reputation (email domains/phone carriers), built heuristics set and machine learning model for the pipeline}
        \resumeItem{Baltar: Improved and maintained a classifier on Verizon Media accounts platform to identify malicious users using machine learning models with Hive, PySpark, Oozie and HDFS}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{\Large Personal Project}
  \resumeSubHeadingListStart
  
    \resumeSubSubheading
      {AI-Powered B2B Hotel Booking Platform}{Dec. 2024 - present}
      \resumeItemListStart
        \resumeItem{Architected and deployed a business travel booking platform that currently serves over 10 companies, supporting 1,000+ MAU and an extensive inventory of thousands of hotels}
        \resumeItem{Engineered an AI agent utilizing agentic workflows and RAG pipelines to automate and streamline hotel booking, trip planning, and inquiry responses directly within a chat application}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{\Large Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rice University}{Houston, TX}
      {Master of Computer Science}{Aug. 2017 -- Dec. 2018}
    \resumeSubheading
      {Tsinghua University}{Beijing, China}
      {Bachelor of Engineering in Microelectronics}{Aug. 2012 -- July 2016}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{\Large Awards and Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Awards}
        {Achieved top 100 national ranking in the 2011 Chinese Physics Olympiad}
    \resumeSubItem{Programming and Frameworks}
      {C++, Java, Python, MLIR, Go, SQL}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}